Poster Data Analysis

### 2018-09-05 notebooks/poster_analysis.Rmd
updated plots and started on MIC plots

@@

# Mutations in intrinsic genes per animal species
```{r}
mut_names <- names(megares_results)

@@

>>>>

# Total MIC profile for all isolates in this study
mic_data <- read.table("../data/total_MIC.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

@@

## Mutations in intrinsic genes per animal species
```{r}
mut_names <- names(megares_results)

@@

## MIC plots
```{r}
test <- megares_results %>%
  left_join(isolate_data, by = "saksnr") %>%
  left_join(isolate_data, by = c("saksnr" = "plate_id")) %>%
  mutate(species.y = if_else(is.na(species.y) == TRUE, species.x, species.y),
         saksnr.y = if_else(is.na(saksnr.y) == TRUE, saksnr, saksnr.y),
         method.y = if_else(is.na(method.y) == TRUE, method.x, method.y),
         NAL.y = if_else(is.na(NAL.y) == TRUE, NAL.x, NAL.y),
         CIP.y = if_else(is.na(CIP.y) == TRUE, CIP.x, CIP.y),
         id = paste(saksnr.y, method.y, sep = "-"),
         dupl = duplicated(id)) %>%
  filter(dupl == FALSE) %>%
  gather(key, value, mut_names) %>%
  group_by(key, value, CIP.y) %>%
  count() %>%
  ungroup() %>%
  mutate(compl = complete.cases(.),
         value = if_else(value == 1, "Mutant", "Wild Type")) %>%
  filter(compl == TRUE) %>%
  spread(value, n, fill = 0)
```
